\Title

### 2016-08-05 manuscript/manuscript.tex
Remove reference to steepest descent

Estimating the Moho depths using the above equations is computationally
costly because of two main factors:
(1) the evaluation and storage of the dense $N \times M$ Jacobian matrix
${\mathbf{A}^k}$
and (2) the solution of the resulting $M \times M$ equation system
(not required for Steepest Descent).
In practice, the derivatives in the Jacobian (Eq.~\ref{eq:jacobian})
are often calculated through a first-order finite-difference approximation.
Thus, evaluating ${\mathbf{A}^k}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
These computations are performed for each iteration of the optimization
of the goal function $\Gamma(\mathbf{p})$.

>>>>

Estimating the Moho depths using the above equations is computationally
costly because of two main factors:
(1) the evaluation and storage of the dense $N \times M$ Jacobian matrix
${\mathbf{A}^k}$
and (2) the solution of the resulting $M \times M$ equation system.
In practice, the derivatives in the Jacobian (Eq.~\ref{eq:jacobian})
are often calculated through a first-order finite-difference approximation.
Thus, evaluating ${\mathbf{A}^k}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
These computations are performed for each iteration of the optimization
of the goal function $\Gamma(\mathbf{p})$.
